Git Learning Notes

### 2014-08-09 ch-tms/tms.tex
tms pl results added

>>>>

PL was examined with core-shell NWs on insulating \ce{SiO2}-Si substrates. A typical Raman spectrum from 160 to 6000 \si{cm^{-1}} is presented in Fig.~\ref{fig:ws2ramall}. This pattern was acquired on the middle spot of the core-shell NW shown as inset. Using 532 nm excitation, the multi-phonon resonant feature was clearly resolved. A broad PL peak was also observed with center at 628 nm and FWHM of 23 nm, corresponding to a photon energy of 1.974 eV with width of 72 meV.

% ws2/wo3 on sio2,1 
\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{ws2_sio2_all}
\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 1]{Raman spectrum acquired on the middle spot of core-shell NW (inset) using 532 nm. The $x$ axis is in logarithmic scale.}
\label{fig:ws2ramall}
\end{figure}

Another feature is the presence of three peaks centering at 1860, 3695, and 5500 \si{cm^{-1}}, respectively, where the latter two is probably the secondary and third overtone of the first peak. The origin of this peak family is still under research. A possible candidate points at the hydrocarbon contamination attached onto the core-shell NWs, as already been observed using TEM imaging. Interesting the intensity of this three-peak family attenuated significantly when using 441 nm excitation, as shown in Fig.~\ref{fig:ws2ramblue}. This comparison suggested there might be some enhancement mechanism from \ce{WS2} resonant Raman vibrations.

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{ws2_sio2_all_blue}
\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 2]{Raman spectrum acquired on the middle spot of core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
\label{fig:ws2ramblue}
\end{figure}

Three Raman sites were chosen to probe possible layer variation using both 532 and 441 nm, with the naming displayed in the inset of Fig.~\ref{fig:ws2ramall}. The Raman patterns are shown in Fig.~\ref{fig:ws2ram3site}a-b. The off-resonance profile in Fig.~\ref{fig:ws2ram3site}b shows only two modes, with $E_{2g}^1$ mode at about 357 \si{cm^{-1}} and $A_{1g}$ mode at $418\sim419$ \si{cm^{-1}}. In contrast, the on-resonance profile in Fig.~\ref{fig:ws2ram3site}a exhibits much richer spectra. The shoulder mode at tip2 spectrum is a manifestation of $B_{1u}$ mode from curved \ce{WS2} layer. According to previous analysis, the apparent ratio between in-plane and out-of-plane vibration indicates site tip2 has multi-wall \ce{WS2}, and the other two possibly have few-wall \ce{WS2}.

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:green}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_green}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:blue}\includegraphics[width=0.45\textwidth]{ws2_sio2_raman_blue}}
\caption[Raman spectrum of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si 3]{Raman scattering from (a) 532 nm and (b) 441 nm excitation scanned along the core-shell NW.}
\label{fig:ws2ram3site}
\end{figure}

This predication is confirmed by the associated PL measurement as displayed in Fig.~\ref{fig:ws2plgreen}. Strong luminescent peaks were found at site mid and tip1, and an extremely weak from site tip2. The PL peaks centered at 1958 and 1934 meV for mid and tip1, respectively. The second and third order peaks also show up on all three Raman sites.

\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{core-shell-sio2-pl_green}
\caption[PL spectra of \ce{WO3}-\ce{WS2} on \ce{SiO2}-Si]{PL spectrum acquired on the core-shell NW shown in the inset of Fig.~\ref{fig:ws2ramall}.}
\label{fig:ws2plgreen}
\end{figure}

### 2014-08-09 figure_table.tex
moo3 draft 50%
minor changes in supp tex files
tms pl results added

@@

@@

@@

>>>>

\si{\degreeCelsius}

@@

\begin{equation}\label{eq:mclns}
\cee{MoCl5(WCl6) + S \rightarrow MoS2(WS2) + S2Cl2}.
\end{equation}

@@

\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.45\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.45\textwidth]{mosemsi_b}}
\caption[Representative morphologies of \ce{MoO3} on Si]{(a) Low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
\label{fig:mosisem}
\end{figure}

@@

\begin{align}
\cee{MB + e_{CB}^- &->[pH<7] MB^{.-} \\
2MB^{.-} &\rightarrow MB + LMB\\
O2 + e_{CB}^- &\rightarrow O2^{.-}}
\end{align}

\begin{align}
\cee{ WS2-WO3 + h\nu &-> e^- + h^+\\
O2 + e^- &-> O2^{.-}\\
OH_{surface}^- + h^+ &-> .OH\\
MB^+ + O2^{.-} + .OH-> \text{degradation phases}
}
\end{align}
